---
title: "Lab5"
author: "Simon Jonsson, Fanny Karelius"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, include = FALSE}
library(lab5)
path <- "2014_riksdagsval_per_valdistrikt.xls"#read_excel("../data/2014_riksdagsval_per_valdistrikt.xls")
```
The package is for the purpose of visualizing the 2014 swedish election results. Provides an interactive shiny app where you can select county and the results for the county. Data is collected from [val.se](http://www.val.se/val/val2014/statistik/index.html).

## General information
Package implements linear regression models, called **linreg** and is called as an example:
```{r, results = "hide"}
viz <- elect_viz$new(path = path)
```

## Methods

Implemented methods are as follows:
**get_counties()** returns a vector of all available counties, used in selection which result to visualize in the Shiny app
```{r}
head(viz$get_counties())
```
**set_county(val)** sets the value of the current county, where val is the county you want to set it to
**get_county()** returns the value of the current county. This is used to select the values you want to plot in the Shiny app
```{r}
viz$get_county()
viz$set_county("Uppsala län")
viz$get_county()
```
**get_mean_p_vals()** returns a named vector with the mean p-values for the county 
```{r}
viz$get_mean_p_vals()
```
